---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# openholidaysR

<!-- badges: start -->
[![R-CMD-check](https://github.com/jfeldhege/openholidaysR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jfeldhege/openholidaysR/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/jfeldhege/openholidaysR/graph/badge.svg)](https://app.codecov.io/gh/jfeldhege/openholidaysR)
[![CRAN status](https://www.r-pkg.org/badges/version/openholidaysR)](https://CRAN.R-project.org/package=openholidaysR)
<!-- badges: end -->

The goal of openholidaysR is to provide dates for public and school holidays for a number of countries and their subdivisions through the OpenHolidays API at https://openholidaysapi.org/.

## Installation

You can install the development version of openholidaysR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("jfeldhege/openholidaysR")
```

## Example

This is a basic example which shows you how to get all public holidays for Germany for January 2025:

```{r example}
library(openholidaysR)

oh_public_holidays(country = "DE",
                   language = "DE",
                   start_date = "2025-01-01",
                   end_date = "2025-01-31")
```


