---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# openholidaysR

<!-- badges: start -->
<!-- badges: end -->

The goal of openholidaysR is to provide dates for public and school holidays for a number of countries and their subdivisions through the OpenHolidays API at https://openholidaysapi.org/.

## Installation

You can install the development version of openholidaysR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("jfeldhege/openholidaysR")
```

## Example

This is a basic example which shows you how to get all public holidays for Germany for the first three months of 2025:

```{r example}
library(openholidaysR)

oh_holidays(country = "DE",
            language = "DE",
            start_date = "2025-01-01",
            end_date = "2025-03-31")
```


